Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration

### 2013-10-08 path_theorems.tex
Small typo corrections.

We can examine the difference in radius $r$ and angle $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conjecture:fastest-paths} to finish our proof. Recall equations \ref{eq:r-deriv-2} and \ref{eq:theta-deriv} which we derived in a previous section. We can use \ref{eq:r-deriv-2} to obtain the following:

\begin{eqnarray}
  \frac{d^2 r_{p_1}(t)}{d t^2} - \frac{d^2 r_{p_2}(t)}{d t^2} = \\
  - sin(| \theta(t_b) |) \left( \bar{a}_c - a^{p_2}_c(t_b) \right) < 0
\end{eqnarray}

@@

We can also use \ref{eq:theta-deriv} to obtain the following for the difference in angles:
\begin{eqnarray}
  \frac{d | \theta_{p_1}(t_b) |}{dt} - \frac{ |\theta_{p_1} (t_b) |}{dt} = \\
  - \frac{1}{v(t_b)} \left(\bar{a}_c - a^{p_2}_c(t_b) \right) < 0
\end{eqnarray}

>>>>

We can examine the difference in radius $r$ and angle $\theta$ between $p_1$ and $p_2$ after $t_b$, and use Conjecture \ref{conjecture:fastest-paths} to finish our proof. Recall equations \ref{eq:r-deriv-2} and \ref{eq:theta-deriv} which we derived in a previous section. We can use equation \ref{eq:r-deriv-2} to obtain the following:

\begin{eqnarray}
  \frac{d^2 r_{p_1}(t)}{d t^2} - \frac{d^2 r_{p_2}(t)}{d t^2} = - \sin(| \theta(t_b) |) \left( \bar{a}_c - a^{p_2}_c(t_b) \right) < 0
\end{eqnarray}

@@

We can also use equation \ref{eq:theta-deriv} to obtain the following for the difference in angles:
\begin{eqnarray}
  \frac{d | \theta_{p_1}(t_b) |}{dt} - \frac{ |\theta_{p_1} (t_b) |}{dt} = - \frac{1}{v(t_b)} \left(\bar{a}_c - a^{p_2}_c(t_b) \right) < 0
\end{eqnarray}
